Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure

### 2020-07-14 CCIAQVTS/CCIAQVTS.tex
removed all non-PRA instances of 'novel'

    The second half of the manuscript, namely \Cref{sec:preliminary_research,sec:found_inequalities,sec:optimizations,sec:fritz_problem_revisit}, presents the main contributions made by this research project. Specifically, in \cref{sec:found_inequalities} we improve upon the results of \citet{Fritz_2012} by offering a direct proof of the incompatibility of the Fritz distribution using inequalities generated by the Inflation Technique~\cite{Inflation}. A sample of such inequalities is presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq}, \cref{eq:web_inequality}, and \cref{eq:symmetric_web_inequality}. Aside from confirming the utility of the Inflation Technique, this paper explores the importance of having derived these inequalities. First, an inequality-based proof has the advantage of being robust to experimental noise. In \cref{sec:violations_noise} the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. Second, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to find the maximum violations achievable by quantum theory. The culmination of these analyses naturally prompts a discussion, found in \Cref{sec:fritz_problem_revisit}, regarding the fundamental problem of recognizing and classifying novel nonclassicality in the Triangle structure. \Cref{sec:conclusions} concludes.

@@

    Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly novel form of nonclassicality for the Triangle structure. Such a discovery would presumably lead to an understanding of different advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open. We attempt to make progress on this problem by leveraging the causal compatibility inequalities derived herein, but \Cref{sec:optimizations} delineates that is effort was plagued by instabilities in our numerical optimization which we have not yet overcome. Consequently, \Cref{sec:fritz_problem_revisit} discusses potential avenues for rigorously reformulating Fritz's problem in order to best capture this desire for novel quantum nonclassicality.

@@

    It is worth noting that there are quantum-accessible distributions which are conjectured, but not proven, to be incompatible with the Triangle structure. For instance, the distribution proposed in~\cite{Gisin_2017} required the use of entangled measurements, and thus if proven incompatible, might constitute a novel form of quantum nonclassicality. Unfortunately, as was previously noted in~\cref{sec:found_inequalities}, the proposed distribution in~\cite{Gisin_2017} satisfies all inequalities generated by the inflations considered in~\cref{fig:inflations}. Presently, computational limitations prevent us from considering larger inflations than those in~\cref{fig:inflations}, although we remain optimistic.

>>>>

    The second half of the manuscript, namely \Cref{sec:preliminary_research,sec:found_inequalities,sec:optimizations,sec:fritz_problem_revisit}, presents the main contributions made by this research project. Specifically, in \cref{sec:found_inequalities} we improve upon the results of \citet{Fritz_2012} by offering a direct proof of the incompatibility of the Fritz distribution using inequalities generated by the Inflation Technique~\cite{Inflation}. A sample of such inequalities is presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq}, \cref{eq:web_inequality}, and \cref{eq:symmetric_web_inequality}. Aside from confirming the utility of the Inflation Technique, this paper explores the importance of having derived these inequalities. First, an inequality-based proof has the advantage of being robust to experimental noise. In \cref{sec:violations_noise} the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities. Second, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to find the maximum violations achievable by quantum theory. The culmination of these analyses naturally prompts a discussion, found in \Cref{sec:fritz_problem_revisit}, regarding the fundamental problem of recognizing and classifying nonclassicality in the Triangle structure. \Cref{sec:conclusions} concludes.

@@

    Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly different form of nonclassicality for the Triangle structure. Such a discovery would presumably lead to an understanding of different advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open. We attempt to make progress on this problem by leveraging the causal compatibility inequalities derived herein, but \Cref{sec:optimizations} delineates that is effort was plagued by instabilities in our numerical optimization which we have not yet overcome. Consequently, \Cref{sec:fritz_problem_revisit} discusses potential avenues for rigorously reformulating Fritz's problem in order to best capture this desire for novel quantum nonclassicality.

@@

    It is worth noting that there are quantum-accessible distributions which are conjectured, but not proven, to be incompatible with the Triangle structure. For instance, the distribution proposed in~\cite{Gisin_2017} required the use of entangled measurements and thus if proven incompatible might constitute a different form of quantum nonclassicality. Unfortunately, as was previously noted in~\cref{sec:found_inequalities}, the proposed distribution in~\cite{Gisin_2017} satisfies all inequalities generated by the inflations considered in~\cref{fig:inflations}. Presently, computational limitations prevent us from considering larger inflations than those in~\cref{fig:inflations}, although we remain optimistic.
